Phenology and Mycorrhizae Manuscript

### 2023-01-30 manuscriptCode_phenologyAndMycorrhizae.Rmd
daily summaries for single air temperature

#Single Air Temperature At Various Heights 
```{r,eval=FALSE}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)

#Triple Air Temperature at Top of Canopy
```{r,eval=FALSE} 
##Need to redownload!! 
dataName="NEON_TemperatureData"
NEON_ID='DP1.00003.001'
selectColumns <- c('tempTripleMean','finalQF')
inFileName <- "TAAT_30min.csv"
varName <- 'tempTripleMean'

@@

#Download NEON Soil Physical and Chemical Properties (Need to finish combining)
```{r,eval=FALSE}
dataName <- "NEON_soilProperties"
NEON_ID <- "DP1.10086.001"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}

>>>>

#Single Air Temperature At Various Heights 
```{r,eval=FALSE}
dataName="NEON_SingleAirTemperature"
NEON_ID='DP1.00002.001'
selectColumns <- c('horizontalPosition','verticalPosition','tempSingleMean','tempSingleExpUncert','finalQF')
inFileName <- "SAAT_30min.csv"
varName <- 'tempSingleMean'

downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=mean,funName="mean")
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=min,funName="min")
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=max,funName="max")
```

#Triple Air Temperature at Top of Canopy
```{r,eval=FALSE} 
##Need to redownload!! 
dataName="NEON_TopTemperatureData"
NEON_ID='DP1.00003.001'
selectColumns <- c('tempTripleMean','finalQF')
inFileName <- "TAAT_30min.csv"
varName <- 'tempTripleMean'
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}

@@

#Download NEON Soil Physical and Chemical Properties
```{r,eval=FALSE}
dataName <- "NEON_soilProperties"
NEON_ID <- "DP1.10086.001"
if(!file.exists(paste0(dataPath,"/",dataName))){
  dir.create(paste0(dataPath,"/",dataName))
}
